\chapter*{Acknowledgments}
	
	First I would like to express the up-most gratitude towards my supervisor Professor Thomas Lumley, Chair in Bio-statistics, Department of Statistics, University of Auckland New Zealand. Who I first meet from STATS 773 Design and Analysis of Clinical Trials back in 2017. Without his supervision and constant guidance over the past year. It would not have been impossible to write my thesis. 
	
	\newpara 
	
	I would also like to thank my family, for all the emotional and financial support they unconditionally provided through my never-ending studies, they had done the best there is for me to have the best chance to success in life. I just hope that my old men would stop thinking that I studied fortune telling (Psychology), and recognise that I actually studied a real, academic subject called Statistics. 

	\newpara
	
	And, many thanks to all the academic and professors from University of Auckland, around new Zealand and all round the world, who provided help and guidance over the past year. Knowledge does not stay in a box, it is everywhere and it produces friendly encounters. 
	
	\newpara 
	
	I would like to extend my warmth to all my friend from psychology, statistics, biological science, education, math and computer science, who struggled through countless overnight assignments, fell asleep together during lecture and panic over exam marks with me.  
	
	\newpara
	
	Lastly, to whoever had the time to spent on my Thesis, thank you for your time, and if you are a postgraduate student who is currently doing a dissertation/Thesis, I wish you good luck.  
	
	\newpara
	
	--- Jung. 
		
		
		
		
		
		
		
